\begin{textsample}{POS Dim 3 – persona\_grok – Score 17.00 – t551\_grok.txt}  \label{ex:f3_pos_037}
The \textbf{car} \textbf{industry} is pushing out increasingly heavier vehicles, such as SUVs, that consume more \textbf{energy} and emit higher \textbf{levels} of CO2.
This \textbf{problem} persists even in electric \textbf{models}, which require larger batteries to power their added weight.
Take the VW Golf as an example : over the decades, its weight has \textbf{increased} significantly, resulting in 57 % more \textbf{emissions}.
The Tiguan, another \textbf{model} from the same manufacturer, is even heavier, exacerbating the issue.
Beyond \textbf{emissions}, these SUVs create greater risks in accidents for pedestrians and other road users. \textbf{Drivers} of these vehicles are also more likely to engage in risky behavior behind the wheel.
Instead of aligning with the goals of the Paris Agreement, the \textbf{industry} is prioritizing profits.
They 're pouring resources into heavy advertising and \textbf{investments} in SUVs, capitalizing on booming \textbf{sales} figures.
We \textbf{need} a \textbf{shift} toward smaller electric \textbf{cars}, along with more shared ownership \textbf{models}, expanded \textbf{public} \textbf{transport} \textbf{options}, and an overall \textbf{reduction} in the \textbf{number} of vehicles on the road.
Greenpeace recently staged a protest against the import of SUVs to draw attention to these concerns and push for change.

% matched lemmas: car, driver, emission, energy, increase, industry, investment, level, model, need, number, option, problem, public, reduction, sale, shift, transport
\end{textsample}
