\begin{textsample}{POS Dim 3 – persona\_grok – Score 18.00 – t536\_grok.txt}  \label{ex:f3_pos_032}
In the fight against plastic pollution, many corporations are touting what they call innovative \textbf{solutions}, but a closer look reveals these often fall short.
Take the switch to \textbf{paper} \textbf{packaging}, for instance—while it might seem like a step away from plastic, it comes at a steep \textbf{cost} to forests, accelerating deforestation and habitat loss.
Then there are bioplastics, promoted as a biodegradable \textbf{alternative}.
However, these \textbf{materials} compete with vital food crops for land and resources, and they don't \textbf{break} down effectively in natural environments, leaving behind persistent \textbf{waste}.
Even recyclable plastics, which sound promising on the surface, face major hurdles.
In reality, they 're seldom actually recycled, and when they are, they 're frequently downcycled into lower-quality \textbf{products}, perpetuating the \textbf{cycle} of \textbf{waste} rather than \textbf{ending} it.
The core issue with these corporate approaches is that they simply \textbf{shift} from one \textbf{material} to another without tackling the root \textbf{problem} : the throwaway \textbf{model} that produces enormous \textbf{amounts} of \textbf{waste} in the first place.
This isn't real progress ; it 's a distraction from meaningful change.
That 's why it 's crucial for \textbf{companies} to \textbf{shift} their focus to genuine \textbf{solutions}.
They must prioritize reducing \textbf{waste} at the source and invest in robust \textbf{reuse} and refill \textbf{systems}.
These strategies offer a path to truly addressing plastic pollution, and they 're exactly what global activists are demanding from corporations worldwide.
By listening to these voices and committing to systemic change, we can move beyond superficial fixes and build a sustainable future.

% matched lemmas: alternative, amount, break, company, cost, cycle, end, material, model, packaging, paper, problem, product, reuse, shift, solution, system, waste
\end{textsample}
