\begin{textsample}{POS Dim 3 – persona\_grok – Score 18.00 – t648\_grok.txt}  \label{ex:f3_pos_036}
As the new year approaches, it 's the perfect \textbf{time} to think about resolutions that not only benefit us personally but also help protect our planet.
At Greenpeace, we 're all about turning \textbf{good} intentions into real action against climate change.
Why not make 2024 the year you commit to eco-friendly resolutions that make a difference? \textbf{Start} by demanding more from our governments.
Push for cities \textbf{designed} with bike lanes and affordable \textbf{public} transportation, and call for phasing out fossil fuel \textbf{cars} to achieve cleaner air for everyone.
On a personal \textbf{level}, consider swapping your \textbf{car} for biking or \textbf{public} \textbf{transport} whenever possible.
This simple switch can reduce \textbf{emissions} while improving your \textbf{health} through more active travel.
Get involved with Greenpeace by volunteering for activism efforts, such as joining marches or occupying oil rigs to challenge fossil fuel \textbf{industries} head-on.
Another powerful resolution : cut back on \textbf{meat} and \textbf{dairy} \textbf{consumption}.
This helps slash \textbf{greenhouse} \textbf{gas} \textbf{emissions} and can boost your \textbf{health} by embracing more plant-based \textbf{diets}.
Finally, reject single-use plastics in your daily life to fight pollution, and urge \textbf{companies} like Coca-Cola and Nestlé to switch to sustainable \textbf{packaging} \textbf{options}.
Together, these steps can drive the change we \textbf{need} for a healthier planet.

% matched lemmas: car, company, consumption, dairy, design, diet, emission, gas, good, greenhouse, health, industry, level, meat, need, option, packaging, public, start, time, transport
\end{textsample}
