\begin{textsample}{POS Dim 3 – human – Score 47.00 – t605\_human.txt}  \label{ex:f3_pos_010}
Monsanto, perhaps the world ’s most reviled environmental villain, has finally been busted for for selling its poisonous \textbf{products} around the world.
In 2010, in New South Wales, Australia, doctors diagnosed farmer Tralee Snape, who had spread Roundup on her fields with her husband Ron, with non-Hodgkin ’s lymphoma ( NHL ).
Australian doctors, including Tralee ’s oncologist, called the disease “ farmer ’s cancer, ” because of the many cases appearing among farmers. “ The bloody bastards who made this \textbf{product} should have warned us, ” Ron Snape says now, “ so we could make an informed decision. ” false \textbf{data} were submitted if test results indicated a \textbf{product} ’s adverse or fatal \textbf{effects}.
One of those convicted was a Monsanto insider Paul L.
Wright.
Wright, for Monsanto attempted to get test results on PCBs altered..
Craven Laboratories, \textbf{used} by Monsanto to test glyphosate … Fraud uncovered in 1990 falsified \textbf{pesticide} residue testing \textbf{data}.. including Roundup Cate Jenkins, 1990, EPA scientist.. suspected Monsanto ’s \textbf{studies} on dioxins were fraudulent claimed “ misrepresentations and falsifications ” in Monsanto ’s \textbf{studies} accused the \textbf{company} of covering up dioxin contamination \textbf{problems} “ obvious fraud ” Mother Jones magazine, Marcia Williams, former EPA \textbf{Pesticide} Review In 2012, after a death from a large dose in Thailand, doctors discovered that the mixture of glyphosate with other compounds in Roundup eroded mucous membrane tissues, gastrointestinal linings, and respiratory tracts, leading to pulmonary congestion and edema in the victim ’s lungs. safety \textbf{data} for \textbf{pesticides} during glyphosate introduction were unsound Carey Gillam, “ Of Mice, Monsanto And A Mysterious Tumor, ” June 8, 2017, Huffington Post, Monsanto.. convince regulators to accept scientific interpretations that support their \textbf{products}. \textbf{company} provided additional \textbf{data} to try to convince the EPA to discount the tumors. 900 cases pending with similar claims – that Monsanto manipulated the science “ Regulatory Collusion, Scientific Mischief, Carey Gillam, Huntington Post, Aug 01, 2017..
Monsanto suppressed \textbf{information} == Food and Water Watch : “ Monsanto Manipulates Science to Make Roundup Appear Safe, ” Monsanto ’s strategy for twisting the science surrounding Roundup.
A 2014 meta-analysis published in the International Journal of Environmental Research and Public Health \textbf{reported} that “ B cell lymphoma was positively associated with … the organophosphorus herbicide glyphosate. ” “ new evidence of Monsanto ’s manipulation of science ” documents reveal a coordinated strategy to manipulate the debate about safety of glyphosate Monsanto commissioned scientists to write favorable \textbf{reviews} of \textbf{studies} Monsanto commissioned panel to counter the WHO ’s classification == Donna R.
Farmer, Ph.D., Toxicology \textbf{Programs}, Monsanto ; US Right to Know “ you cannot say that Roundup is not a carcinogen … we have not done the necessary testing on the formulation to make that statement. … we advise \textbf{using} the phrase …. ‘ no unreasonable adverse \textbf{effects} to people, wildlife, and the environment are expected. ” This misrepresent lab test results by adding “ unreasonable. ” == Baum Hedlund Aristei Goldman, attorneys, firm website “ Monsanto has known Roundup … is carcinogenic for several decades, but buried the risks … “ EPA determined that laboratories hired by Monsanto.. committed fraud.
In February, this year, a meta-analysis by Louping Zhang and colleagues at the University of Washington, found “ a compelling link between exposures to GBHs ( glyphosate-based herbicides ) and \textbf{increased} risk for NHL ( non-Hodgkins lymphoma ). ” attorney Brent Wisner : Monsanto stopping \textbf{studies} that look bad for them == GM-Free Cymru, Wales, UK, gmfreecymru.org : fraud in Roundup / Glyphosate testing Craven Laboratories, for Monsanto, falsified test result falsifying notebook entries manipulating scientific equipment to produce false \textbf{reports}.
Roundup residue \textbf{studies} among the tests in question. == NB Media Co-op citing Journal of Public Health Policy : Monsanto manipulated glyphosate approval process, by Dallas McQuarrie on August 13, 2018 Monsanto attempted to manipulate scientific evidence for its own \textbf{business} interests. == The secret tactics Monsanto \textbf{used} to protect Roundup, ” ABC Australia, 2018 In 2016, the US Environmental Protection Agency ( EPA ) concluded that glyphosate had “ low toxicity for humans. ” However, critics have claimed that Monsanto exercised undue influence on that \textbf{study}, which is now under \textbf{review}.
Former EPA advisors recently found people heavily exposed to Roundup are 41 % more likely than unexposed individuals to develop non-Hodgkins lymphoma.
The World Health Organization classifies glyphosate as “ probably carcinogenic to humans, ” while the state of California says it is “ known to cause cancer. ” Carry Gillam : “ scientific literature has been corrupted ” Monsanto Papers,.. “ the \textbf{company} has worked to hide the risks of its \textbf{products} ” Laboratory was doctoring the \textbf{numbers}, cooking the books.. fraudulent \textbf{studies}.. an aggressive campaign of deception and dirty tricks. “ EPA declared the \textbf{studies} invalid, flawed science Craven labs ( for Monsanto ) caught falsifying test results for … Roundup. “ Bullying ” scientists : Perhaps the most compelling evidence is \textbf{reviewed} in the Le Monde article from 2017.
There appears to be evidence that Monsanto “ targeted ” \textbf{studies} they did not like, attempted to “ destroy ” the UN cancer agency ( IARC ), “ vilified ” and attempted to “ discredit ” the agency and individual scientists, “ intimidated, ” sought to “ install anxiety, ” “ bullied, ” sought “ maliciously ” to “ cut off funding, ” “ smeared ” reputations, “ undermined ” scientists, agencies and their \textbf{studies}, and engaged in “ arm-twisting, ” and “ strong-arming, ” scientists.
IARC : “ Monsanto \textbf{papers} : la guerre du géant des \textbf{pesticides} contre la science, ” Le Monde, Stéphane Horel, Stéphane Foucart, June 2017.
In March 2015, the World Health Organization ’s International Agency for Research on Cancer ( IARC ) \textbf{reviewed} the scientific \textbf{data} regarding glyphosate.
IARC avoided unpublished industry-funded \textbf{studies}, whereas the EPA had allowed Monsanto to submit their own unpublished research.
Based on epidemiological \textbf{studies}, animal \textbf{studies}, and in-vitro \textbf{studies}, IARC classified glyphosate in category 2A, as “ probably carcinogenic in humans. ” English version : Monsanto Papers : An investigation on the worldwide war the Monsanto has \textbf{started} in order to save glyphosate, Environmental Health News, Nov. 2017. “ Monsanto corporation has undertaken an effort to destroy the United Nations ’ cancer agency, ” Christopher Wild, IARC Scientist : “ we are the target of an orchestrated campaign of an unseen \textbf{scale} and duration. ” “ unprecedented brutality. ” Monsanto vilified IARC ’s work as “ junk science. ” Pathologist Consolato Maria Sergi, University of Alberta in Canada, wrote, November 4, 2016, concerning a letter Monsanto sent to individual scientists who worked for IARC : “ I found your letter intimidating and noxious..
I find your approach reprehensive and lacking in common courtesy even by today ’s \textbf{standards}. … I consider your letter pernicious because it maliciouslyseeks to instill some anxiety and apprehension in an independent group of experts. ” “ Bully Monsanto attacks scientists who link Glyphosate and cancer, ” The Hill, C.
Gillam, 2016 Monsanto via “ CropLife America ” are driving efforts to cut off U.S. funding for IARC Monsanto labeled IARC findings as “ junk science, ” With international \textbf{studies} stacking up and regulators warning potential victims, Monsanto went on a \textbf{public} relations offensive. \textbf{Company} lobbyists called the IARC \textbf{report} biased and demanded a retraction.
They claimed IARC “ purposefully disregarded dozens of scientific \textbf{studies}, ” namely the unpublished industry-funded \textbf{studies}.
In 2012, Monsanto founded and led the “ Glyphosate Task Force, ” a consortium of \textbf{companies} promoting glyphosate in Europe.
After the IARC decisions, this \textbf{industry} group attacked the IARC for scientific “ deficiencies. ” claims IARC members are part of an “ unelected, undemocratic, foreign body. ” Monsanto tactics overwhelming for IARC scientists.. not accustomed to assaults on their character.
IARC statement.. saying some scientists felt “ intimidated ” by the \textbf{industry} actions..
Australian epidemiologist Lin Fritschi : attacks on the team ’s credibility are unwarranted.
Monsanto documents reveal : a \textbf{public} relations effort to discredit the IARC \textbf{report} Monsanto ’s \textbf{public} relations plan to “ orchestrate outcry ” Guardian OEHHA harassment suit : 2015, California Office of Environmental Health Hazard Assessment ( OEHHA ) announced plans to \textbf{list} glyphosate as a carcinogen, Monsanto sued OEHHA and its director, Lauren Zeise, lost the case, but created threat, work load, and \textbf{costs} to OEHHA.
Edwin Hardeman case before Chabria : undermining anyone who raises genuine and legitimate concerns about the issue. ” DeWayne Johnson case : “ Monsanto has specifically gone out of its way to bully … and to fight independent \textbf{researchers}, ” said the attorney Brent Wisner Internal Monsanto documents revealed that an editorial in Forbes magazine, by an academic challenging the \textbf{report}, had been ghostwritten by Monsanto.
The academic had not revealed Monsanto ’s involvement.
In response, Forbes removed the editorial.
Monsanto ‘ bullied scientists ‘ and hid weedkiller cancer risk, lawyer tells court : Guardian Monsanto … resorted to bullying independent \textbf{researchers} ( citing lawyers ) Mercola Health Carey Gillam, Whitewash, 2017. scientists reputations have been smeared for publishing research that contradicted \textbf{business} interests.
Publisher writes : Readers learn about the arm-twisting of regulators blackballing critics and strong-arming regulators.
Bayer, Nazis, and Zyklon \textbf{gas} : added references for Bayer ’s Zyklon \textbf{gas} affiliation.
I added the United Nations War Crimes Commission, link.
Clarify court vs. scientific evidence : This paragraph is a summary of what is to come, wherein I do distinguish the court decisions from the science.
Here, however, I am simply summarizing what is about to be detailed.
I ’ve changed “ revealed ” to — “ have resulted in accusations by victims, scientists, and media that ” — which simply \textbf{reports} the accusations. rat \textbf{studies} : I reference Carey Gillam, from her book, “ Whitewash : The Story of a Weed Killer, Cancer, and the Corruption of Science, ” and her article “ Of Mice, Monsanto And A Mysterious Tumor, June 8, 2017, Huffington Post, to which I ’ve linked, and I ’ve cited her and this article as the reference.
Gillam goes thoroughly into the history of this \textbf{study}, and writes a book on it.
For the purpose of this article, I cite her research, “ according to ” Gillam.
The bit about ” Children are particularly vulnerable, ” is a generalized statement that appears in some \textbf{studies} and \textbf{reviews}, and is generally true regarding any toxic poisoning. change glyphosate to organo-phosphate \textbf{pesticides}, re : 2001 US National Cancer Institute \textbf{study}.
In 2016, after California ’s Office of Environmental Health Hazard Assessment ( OEHHA ) announced plans to \textbf{list} glyphosate as a known carcinogen, Monsanto launched a SLAPP lawsuit against OEHHA and its director, Lauren Zeise.
Monsanto lost the suit after spending a year harassing the regulator.
Clarify Thailand incident, large dose : I point out that the Thailand exposure was a “ large dose, ” and that the significant revelation from this case is that the mixture of glyphosate with other compounds led to the \textbf{health} impact.
I cite the relevant \textbf{study} in the American Journal of Forensic Medical Pathology so that any interested reader \textbf{may} dig deeper.
Address \textbf{review} \textbf{studies} : I point out that the International Journal of Environmental Research and Mutation Research \textbf{papers} are both meta-studies, \textbf{reviews} of a collection of \textbf{studies}, and I quote them directly.
Glyphosate Task Force : I ’ve added the 2012-2015 timeline and identified this as a consortium of \textbf{companies}.
Source original DOA \textbf{report}, re : EWG \textbf{report} : I clarify that EWG \textbf{study} is a \textbf{review} \textbf{study}, and add the DOA \textbf{report} link.
Qualify language regarding EWG, DOA, French and Canadian \textbf{researchers} regarding the value of organic food. added DOA \textbf{report} link Regarding the Canadian honey stuty, I cited the original \textbf{study}, and add it to the references at the \textbf{end}. “ Determination of glyphosate, AMPA, and glufosinate in honey by online solid-phase extraction-liquid chromatography-tandem mass spectrometry, ” Thomas S.
Thompson, et al., Agri-Food Laboratories, Alberta, Canada, Journal of Food Additives \& Contaminants, v. 36, 19 Feb. 2019.
Regarding the French \textbf{study}, I am only \textbf{reporting} the association they \textbf{report} : organic food eaters had fewer cancers.
Their qualifying language does not \textbf{need} to be quoted, since most such \textbf{studies} rigorously qualify results.
I added a reference re : declining nutrition.
The \textbf{increase} of environmental toxins and cancer \textbf{rates} since 1950 ( the \textbf{beginning} of the so-called “ Green Revolution ” ) is generally well known and probably does not \textbf{need} a reference.
The decline in nutrients is also well known, and supported in many \textbf{studies}.
In any case, I ’ve cited : “ Declining Fruit and Vegetable Nutrient Composition : What Is the Evidence? ” American Society for Horticultural Science, Donald R.
Davis, 2009.
This \textbf{study} references three kinds of evidence in the US \& UK : In 2017, journalist Carey Gillam published “ Whitewash : The Story of a Weed Killer, Cancer, and the Corruption of Science. ” Gillam \textbf{used} Monsanto ’s own internal documents to show that the \textbf{company} smeared the reputations of scientists who published research that challenged their statements, threatened regulators to approve the \textbf{chemical}, skipped compliance tests, and \textbf{used} the media to manipulate \textbf{public} perception. 1 ) early \textbf{studies} of fertilization found inverse relationships between crop yield and \textbf{mineral} concentrations—the widely cited “ dilution \textbf{effect} ” ; 2 ) three \textbf{studies} of historical food composition \textbf{data} found apparent median declines of 5 % to 40 % or more in some \textbf{minerals} in groups of vegetables and perhaps fruits 3 ) recent side-by-side plantings of low- and high-yield cultivars of broccoli and grains found consistently negative correlations between yield and concentrations of \textbf{minerals} and protein, a newly recognized genetic dilution \textbf{effect}... this topic has been widely treated in popular media, such as : “ A Decline in the Nutritional Value of Crops, ” New York Times : Worldwatch Institute : “ Farmers today can grow two to three \textbf{times} as much grain, fruit, and vegetables on a plot of land as they could 50 years ago, but the nutritional \textbf{quality} of many crops has declined, ” based on a \textbf{report} co-authored by Worldwatch Institute food \textbf{researcher} Brian Halweil. “ Less nutrition per calorie consumed affects \textbf{consumers} in much in the same way as monetary inflation ; that is, we have more food, but it ’s worth less in \textbf{terms} of nutritional value. ” reference for David Wallace-Wells, quote re : decline of protein, calcium, iron, vitamin C in food.
Quotes from D.
Wallace-Wells, from “ The Uninhabitable Earth. ” Goodreads Juries in three U.S. lawsuits in the last year have ruled that Monsanto ’s glyphosate-based Roundup herbicide caused or significantly contributed to the onset of non-Hodgkin ’s lymphoma, a life-threatening immune \textbf{system} cancer.
Over US\$2-billion has been awarded in damages to four victims, and over 13,000 other lawsuits are now pending.
Oncologist, Dr.
Brian Durie, Chairman of the International Myeloma Foundation, in support of Gillam, noted that Monsanto was guilty of “ ruthless greed and fraud which have led to the poisoning of our planet. ” According to David Schubert, Head of the Cellular Neurobiology Laboratory at the Salk Institute for Biological Studies, “ Monsanto and other agricultural \textbf{chemical} \textbf{companies} lied about their \textbf{products}, covered up the damaging \textbf{data}, and corrupted government officials in order to sell their toxic \textbf{products} around the world. ” Among their favorite catchphrases, Monsanto claimed that glyphosate was “ safe enough to drink. ” Publicist Patrick Moore, who describes Monsanto as “ a seed \textbf{company} that offers crop protection, ” often repeated this slogan but eventually got caught in the deceit.
In March 2015, Moore appeared on French cable \textbf{news} station Canal+ and announced, “ glyphosate is not causing cancer.
You can drink a whole quart of it, and it won't hurt you. ” The Canal+ journalist replied, “ Would you like to drink some?
I have some. ” “ I \textbf{’d} be happy to, ” said Moore, then appeared dazed and confused. “ Not really, ” he stumbled, “ I ’m not stupid. ” “ So, ” replied the journalist, “ you know it ’s dangerous. ” Moore backtracked again, claiming, “ It ’s not dangerous to humans. ” However, when the journalist again offered him a glass of glyphosate, the bewildered lobbyist fled the interview, declaring, “ No, I ’m not an idiot. ” In the case of Edwin Hardeman, 70, who acquired non-Hodgkin ’s lymphoma after long exposure to glyphosate, a US federal court found that Monsanto had defectively \textbf{designed} Roundup, acted negligently, failed to warn \textbf{customers} of the cancer risk, and had engaged in deliberate, underhanded efforts to influence scientists and regulators concerning the safety of glyphosate.
Judge Vince Chhabria rebuked the \textbf{company}, saying “ There is strong evidence from which a jury could conclude that Monsanto does not particularly care whether its \textbf{product} is in \textbf{fact} giving people cancer, focusing instead on manipulating \textbf{public} opinion and undermining anyone who raises genuine and legitimate concerns about the issue. ” The risk of \textbf{pesticides} in food does not stop with glyphosate.
A 2019 \textbf{review} \textbf{study} by the US Environmental Working Group ( EWG ) — based on a 2018 US Department of Agriculture ( DOA ) \textbf{report} — documented \textbf{pesticide} residues in 70 % of produce sold in US even after washing.
The DOA found 225 different \textbf{pesticides} in common fruits and vegetables that had been peeled and washed.
The twelve most contaminated \textbf{products} were strawberries, spinach, kale, nectarines, apples, grapes, peaches, cherries, pears, tomatoes, celery, and potatoes.
The most frequently detected \textbf{pesticide} was Dacthal, DCPA, classified by the US Environmental Protection Agency as a possible human carcinogen, and prohibited in Europe since 2009.
A French \textbf{study} among 69,000 citizens, published last year, found that people who most frequently ate organic food had 25 % fewer cancers than those who did not eat organic food.
A Canadian \textbf{study} found glyphosate in 98 % of Canadian honey samples.
The EWG, DOA, and the French and Canadian \textbf{researchers} all warn that to avoid \textbf{pesticides} and genetically modified foods, citizens would benefit by eating organic produce.
According to David Wallace-Wells, “ Since 1950, much of the \textbf{good} \textbf{stuff} in the plants we grow – protein, calcium, iron, vitamin C, just to name four – has decline by around one third.
Everything is becoming more like junk food.
Even the protein content of bee pollen has dropped by a third. ” The so-called “ green \textbf{revolution} ” in \textbf{agriculture} has helped produce an \textbf{increased} quantity of food, but the \textbf{cost} has been a sharp decline in nutrition and a dangerous \textbf{increase} in poisons and cancer \textbf{rates}.
Only a few generations ago, what we now call “ organic farming, ” was just called “ farming. ” A year ago, well aware of the imminent medical liabilities, the German \textbf{chemical} and drug giant, Bayer AG, bought the troubled Monsanto.
Since the purchase, as Monsanto ’s liabilities mounted, Bayer ’s stock \textbf{price} has plummeted, losing over 40 % of its value.
Pesticide-based farming — led by \textbf{companies} such as Monsanto, dating back to the days of DDT \textbf{use} and Rachel Carson ’s “ Silent Spring ” warning — has left behind a trail of unintended consequences. “ Monsanto must pay couple \$2bn in largest verdict yet over cancer claims, Guardian, 13 May, 2019. “ Roundup : Bayer condamné à payer 2 milliards de \textbf{dollars} à un couple américain, 13 May, 2019, Le Monde.
Bayer ’s involvement with IG Farben, Zyklon \textbf{gas}, and Nazi concentration camps : United Nations War Crimes Commission, “ IG Farben and Krupp trials ” ; New York Times, “ Feared Symbol of Nazi Era Seeks Bankruptcy, by Mark Landlernov, 2003 ; Nurenberg Tribunal, “ The IG Farben Case, ” p. 1282 ; Peoplesworld.org, “ Bayer-Monsanto merger can't erase Nazi chemists ’ past, ” September 22, 2016, by Victor Grossman.
Monsanto accused of manipulating laboratory results : “ Monsanto Weed Killer Roundup Faces New \textbf{Doubts} on Safety in Unsealed Documents, ” Danny Hakim, New York Times, March 14, 2017 ; and “ \textbf{industry} manipulated academic research or misstate findings, The New York Times, 2018. “ Whitewash : The Story of a Weed Killer, Cancer, and the Corruption of Science, ” by Carey Gillam, Island Press, 2017. “ Monsanto Manipulates Science to Make Roundup Appear Safe, ” Food and Water Watch, April, 2017. “ laboratories hired by Monsanto to conduct Roundup \textbf{studies} committed fraud Baum Hedlund Aristei Goldman, attorneys, firm website.
The secret tactics Monsanto \textbf{used} to protect Roundup, ” ABC Australia, 2018.
International Monsanto tribunal http://www.monsanto-tribunal.org/.
Monsanto accused of bullying scientists : “ Monsanto \textbf{papers} : la guerre du géant des \textbf{pesticides} contre la science, Le Monde, Stéphane Horel, Stéphane Foucart, June 2017 ; and an English version : “ Monsanto Papers : An investigation on the worldwide war the Monsanto corporation has \textbf{started} in order to save glyphosate, ” Environmental Health News, Nov. 2017. “ Bully Monsanto attacks scientists who link Glyphosate and cancer, ” The Hill, Carey Gillam, 2016.
Monsanto “ ‘ bullied scientists ” and hid weedkiller cancer risk, lawyer tells court : Guardian.
International Monsanto Tribunal, 2016-2017, Den Haag, Netherlands.
Five judges ruled that Monsanto ( Bayer ) activities have a negative impact on basic human rights. “ Exposure to Glyphosate-Based Herbicides and Risk for Non-Hodgkin Lymphoma : A Meta-Analysis and Supporting Evidence, Luoping Zhang, Iemaan Rana, Rachel M.Shaffer, et al., University of Washington, \textbf{Reviews} in Mutation Research, 19 February 2019. “ Pathological and toxicological findings in glyphosate-surfactant herbicide fatality : a case \textbf{report}, ” Sribanditmongkol P., et. al., The American Journal of Forensic Medicine and Pathology, NCBI, 2012.
Glyphosate General \textbf{Fact} Sheet, Henderson, A.
M. ; et al.
National \textbf{Pesticide} Information Center, Oregon State University, NPIC, 2010. “ Non-Hodgkin lymphoma and occupational exposure to agricultural \textbf{pesticide} \textbf{chemical} groups and active ingredients : a systematic \textbf{review} and meta-analysis, ” Schinasi L, Leon M.
International Journal of Environmental Research and Public Health, 2014.
Bayer ’s own dubious history includes an affiliation with IG Farben in producing Zyklon B \textbf{gas} for Hitler ’s execution camps and conducting deadly medical experiments on prisoners.
Typically, after the glyphosate trials, Bayer doubled down on denial. “ Glyphosate-based herbicides do not cause cancer, ” claimed spokesman Dan Childs, insisting that “ Monsanto ’s conduct has been appropriate. ” Bayer \textbf{may} soon have to eat those words. “ Agricultural \textbf{use} of organophosphate \textbf{pesticides} and the risk of non-Hodgkin ’s lymphoma among male farmers ( United States ), ” Waddell B.L., et al., Division of Cancer Epidemiology and Genetics, US National Cancer Institute, Cancer Causes Control, 2001.
Monsanto Emails Raise Issue of Influencing Research on Roundup Weed Killer, ” New York Times, 2017.
IARC Monograph on Glyphosate, WHO, 2015. “ Common weed killer glyphosate \textbf{increases} cancer risk by 41 %, ” Emily Dixon, CNN, February 15, 2019 “ Roundup substantial \textbf{factor} in man ’s cancer, jury finds in key verdict, ” The Guardian, March 19, 2019. “ Bayer must pay another \$80mn in Monsanto Roundup cancer trial, ” Reuters / Wolfgang Rattay, RT News, 28 March, 2019, “ Widely \textbf{used} herbicide linked to cancer ” Cressey D ( March 25, 2015 ).
Nature, 2015. ” malathion, diazinon and glyphosate — were \textbf{rated} as “ probably carcinogenic to humans. ” “ Differences in the carcinogenic evaluation of glyphosate between the International Agency for Research on Cancer ( IARC ) and the European Food Safety Authority ( EFSA ), ” Portier CJ, Armstrong B.K., et al. ( 94 medical research scientists ), Journal of Epidemiology and Community Health, 2016. “ Carcinogenicity of tetrachlorvinphos, parathion, malathion, diazinon, and glyphosate, ” Kathryn Z.
Guyton. et al., The Lancet, Oncology, 2015. “ Weed Killer, Long Cleared, Is \textbf{Doubted}, ” Andrew Pollack, New York Times, 27 March 2015.
The three landmark court cases, and subsequent investigations, that brought down Monsanto, and \textbf{may} ultimately bring down Bayer, have resulted in accusations by victims, scientists, and media that, to promote the \textbf{sale} of glyphosate, Monsanto suppressed evidence, manipulated lab results, bullied and harassed scientists, and undermined international regulators.
Internal documents obtained by the courts now suggest that Monsanto \textbf{marketed} Roundup as “ safe, ” knowing full well that it was a likely carcinogen. “ Association Between \textbf{Pesticide} Residue Intake from \textbf{Consumption} of Fruits and Vegetables and Pregnancy Outcomes Among Women Undergoing Infertility Treatment With Assistance Reproductive Technology, ” Y-H Chiu, et al.,.
JAMA Internal Medicine, 2018. “ Monsanto Lobbyist Runs Away When Asked To Drink ‘ Harmless ’ \textbf{Pesticide}, ” Pat Moore caught lying, flees Canal+ interview, The Young Turks, March 2015.
The secret tactics Monsanto \textbf{used} to protect Roundup, ” ABC Australia, 2018 “ Whitewash : The Story of a Weed Killer, Cancer, and the Corruption of Science, ” by Carey Gillam, Island Press, 2017. “ Of Mice, Monsanto And A Mysterious Tumor, June 8, 2017, Carey Gillam Huffington Post, \textbf{Pesticide} residues found in 70 % of produce sold in US, EWG \textbf{review} \textbf{study}, March 2019, based on a December 2018 US Department of Agriculture ( DOA ) \textbf{report}. “ Weed killer residues found in 98 percent of Canadian honey samples, ” Carey Gillam, Environmental Health News, March, 2019 “ Association of Frequency of Organic Food \textbf{Consumption} with Cancer Risk, ” Baudry et al., JAMA, Internal Medicine, 2018. “ Estimating \textbf{Pesticide} Exposure from Dietary Intake and Organic Food Choices : The Multi-Ethnic \textbf{Study} of Atherosclerosis ( MESA ), ” C.L.
Curl et al., Environmental Health Perspectives, 2015. “ Organic Diet Intervention Significantly Reduces Urinary \textbf{Pesticide} Levels in U.S.
Children and Adults, C.
Hyland et al., Environmental Research, 2019.
In 1950, Swiss chemist Henry Martin first synthesized glyphosate, a \textbf{chemical} analogue of the natural amino acid, glycine.
Glyphosate acts as a non-selective herbicide, killing most plants and some micro-organisms by disrupting a \textbf{chemical} \textbf{pathway} that produces essential amino acids.
Since mammals do not contain this particular \textbf{chemical} \textbf{pathway}, Monsanto, without waiting for definitive test results, originally claimed the \textbf{chemical} “ is safer than table salt. ” They began \textbf{marketing} the herbicide as “ Roundup ” in 1974.
California Department of \textbf{Pesticide} \textbf{Regulation}, \textbf{Pesticide} Residues on Fresh Produce, CDPA, 2015. “ Determination of glyphosate, AMPA, and glufosinate in honey by online solid-phase extraction-liquid chromatography-tandem mass spectrometry, ” Thomas S.
Thompson, et al., Agri-Food Laboratories, Alberta, Canada, Journal of Food Additives \& Contaminants, v. 36, 19 Feb. 2019.
Quotes from D.
Wallace-Wells, from “ The Uninhabitable Earth. ” Goodreads “ Declining Fruit and Vegetable Nutrient Composition : What Is the Evidence?, ” American Society for Horticultural Science, Donald R.
Davis, 2009.
This blog has been republished with the following edits and notes from the author : In this piece, I am not setting out to prove that Monsanto ’s glyphosate \textbf{product} Roundup is dangerous, although I believe the evidence supports that conclusion.
I am \textbf{reporting} on court decisions that have ruled Monsanto liability for injury due to their \textbf{products} ; and I am \textbf{reporting} on allegations of their undue influence on, and manipulation of, the scientific and regulatory process.
Links : Added direct links throughout. added direct link to : Juries in two ( now three ) U.S. lawsuits in the last year have ruled that Monsanto ’s glyphosate-based Roundup herbicide caused or significantly contributed to the onset of non-Hodgkin ’s lymphoma, a life-threatening immune \textbf{system} cancer. added International Monsanto tribuna l to the \textbf{end} references EPA : Clarify EPA vs IARC decisions, credibility of EPA decision and Monsanto ’s manipulation of science, balance in the narrative.
Here is a summary of some of the evidence of Monsanto ’s manipulation of the science, certain \textbf{studies}, the EPA decision, and other regulatory decisions.
Given these numerous references to Monsanto ’s manipulation, the legal team is satisfied with the claims made in this article. : In the 1990s, Monsanto labs found a bacteria strain that could survive in glyphosate, cloned the relevant enzyme gene sequence into soybeans and introduced the first glyphosate-resistant plants that allowed farmers to poison weeds without killing the cash crop.
The technique has since been applied to maize, canola, alfalfa, sugar beets, and cotton.
By 2015, in the US, 94 % of soybeans and 89 % of corn and cotton were genetically modified to be glyphosate-tolerant. == New York Times : 2018 \textbf{review} by The New York Times \textbf{industry} manipulates academic research or misstate findings. example : Monsanto-financed \textbf{paper} on glyphosate Monsanto picked scientists and shaped the project.
Monsanto Influencing Research on Roundup … NY Times “ Monsanto..
Roundup Faces New \textbf{Doubts} on Safety ” : New York Times, March 14, 2017 re : files unsealed by Judge Vince Chhabria : raising questions about.. research practices of Monsanto Monsanto had ghostwritten research attributed to academics However, the “ safer than salt, ” slogan soon began to collapse.
As documented by journalist Carey Gillam, scientists linked repeated or high doses administered to rats during pregnancy to stunted \textbf{growth} and bone defects in fetuses.
Children are particularly vulnerable, as their bodies and organs are actively growing. academic research it underwrites is compromised == Carey Gillam : “ Whitewash : The Story of a Weed Killer, Cancer, and the Corruption of Science, ” Island Press, 2017.
David Schubert, Salk Institute ( citing Gillam ) : “ Monsanto lied.. covered up damaging \textbf{data} Marion Nestle, New York University, ( citing Gillam ) : “ Monsanto-paid scientists … influenced EPA make Roundup appear benign in the face of evidence that glyphosate is carcinogenic.. manipulation of science Excerpt at Google Scholar the \textbf{company} arranged for Marvin Kuschner to.. persuade the agency Skin lesions, headaches, and respiratory symptoms first began to appear among farmers.
A 2001 US National Cancer Institute \textbf{study} among male farmers showed “ a statistically significant 50 % \textbf{increased} risk ” of non-Hodgkin ’s lymphoma after exposure to organophosphate \textbf{pesticides}, such as Roundup. that the observed tutors are not related to glyphosate Levinskas … efforts … to downplay damaging findings Monsanto refused to repeat \textbf{studies} as requested EPA ’s toxicology branch expressed \textbf{doubts} about the validity of Monsanto ’s \textbf{data} The 1983 \textbf{study} that showed kidney tumors in mice.. a Monsanto trade secret. only scientists with financial ties to Monsanto affirmed … a tumor in the \textbf{control} group research Monsanto provided to the EPA raised red flags.. because fraud had been discovered deceptions by Monsanto ’s hired labs Industrial Bio-Test Laboratories ( IBT ) the FDA discovered deception convicted of trying to defraud the government by covering up inaccurate research \textbf{data}.

% matched lemmas: agriculture, beginning, business, chemical, company, consumer, consumption, control, cost, customer, datum, design, dollar, doubt, effect, end, fact, factor, gas, good, growth, health, increase, industry, information, list, market, may, mineral, need, news, number, paper, pathway, pesticide, price, problem, product, program, public, quality, rate, regulation, report, researcher, review, revolution, sale, scale, standard, start, study, stuff, system, term, time, use, will
\end{textsample}
