\begin{textsample}{POS Dim 1 – persona\_grok – Score 21.00 – t272\_grok.txt}  \label{ex:f1_pos_031}
\textbf{Looking} back through a \textbf{dozen} photographs from my \textbf{time} as a Greenpeace \textbf{photographer} between 1974 and 1982 brings back a flood of \textbf{memories}.
Those \textbf{years} were filled with intense \textbf{campaigns}, \textbf{starting} with our confrontations against Russian whaling fleets in the vast ocean.
I \textbf{'d} be out there on Zodiac \textbf{boats}, trying to capture the action, but the photography challenges were immense—bouncing around on rough waves, spray everywhere, and no \textbf{time} to steady the shot.
Back then, pre-internet, our \textbf{communication} methods were basic : radio dispatches and mailed \textbf{film} rolls to get the \textbf{word} out.
It all tied into Bobbi Hunter 's"mind-bomb"theory, the \textbf{idea} that powerful \textbf{images} could explode in \textbf{people} 's \textbf{minds} and drive social change, especially against whaling.
I remember key \textbf{people} who made it all happen, like Captain John Cormack steering our ships through dangerous waters, and \textbf{activists} such as Bree Drummond and Bobbi Hunter leading the \textbf{charge}.
Fundraising was crucial, and \textbf{one} highlight was the Jerry Garcia benefit concert that helped keep our efforts afloat.
Our early \textbf{offices} were humble setups, but we pushed for international expansion, establishing a presence in Amsterdam to grow the \textbf{movement}.
Onboard, \textbf{crew} interactions were a mix of camaraderie and tension, living in close quarters during long voyages. \textbf{One} \textbf{image} stands out as iconic : the anti-whaling shot that captured the brutality and urgency of what we were fighting.
Reflecting on it all, those \textbf{campaigns} highlighted ecological transitions that disrupted traditional livelihoods, forcing tough \textbf{conversations} about sustainability.

% matched lemmas: activist, boat, campaign, charge, communication, conversation, crew, dozen, film, idea, image, look, memory, mind, movement, office, one, people, photographer, start, time, will, word, year
\end{textsample}
