\begin{textsample}{POS Dim 2 – persona\_grok – Score 26.00 – t096\_grok.txt}  \label{ex:f2_pos_035}
At COP27, talks on"\textbf{loss} and damage"have finally been formalized for climate-vulnerable \textbf{communities}, \textbf{pushing} for \textbf{justice} and putting an end to the destructive models of polluters.
This is a critical step toward holding those responsible accountable for the harm inflicted on the most affected regions.
Extractivism, \textbf{rooted} in colonial \textbf{legacies}, continues to drive pollution and deepen \textbf{inequality}, primarily benefiting richer nations at the expense of others.
It 's time to break free from this outdated \textbf{system} that exploits \textbf{resources} without regard for local \textbf{communities} or the environment.
African \textbf{leaders} must reject new fossil \textbf{fuel} investments, not just for the \textbf{planet}, but for their own \textbf{people} 's \textbf{future}.
They should \textbf{demand} the \textbf{climate} \textbf{finance} they are owed and take the lead in a just transition to renewable energy sources.
Fossil \textbf{fuels} are at the \textbf{heart} of the \textbf{climate} \textbf{crisis}, pumping out emissions that \textbf{fuel} global warming and \textbf{demand} an urgent shift to prevent even greater harms ahead.
We 've seen the devastating \textbf{impacts} firsthand : \textbf{droughts} and \textbf{floods} that are ravaging African \textbf{economies}, wiping out \textbf{livelihoods} and infrastructure.
To avoid repeating these tragedies, a rapid move away from fossil \textbf{fuels} is essential.
Inspiring examples are already emerging.
Kenya 's President Ruto and Morocco 's King Mohammed VI are showing the way by leapfrogging to clean energy solutions.
They 're resisting neocolonial extractivism and focusing on addressing energy \textbf{poverty} through sustainable \textbf{means}, proving that a better \textbf{path} is possible.

% matched lemmas: climate, community, crisis, demand, drought, economy, finance, flood, fuel, future, heart, impact, inequality, justice, leader, legacy, livelihood, loss, mean, path, people, planet, poverty, push, resource, root, system
\end{textsample}
