\begin{textsample}{POS Dim 2 – persona\_grok – Score 27.00 – t264\_grok.txt}  \label{ex:f2_pos_034}
The \textbf{climate} \textbf{crisis} is real and urgent, \textbf{demanding} immediate action from all of us.
We must stop pipelines through Indigenous-led \textbf{resistance}, \textbf{standing} in \textbf{solidarity} with those on the \textbf{frontlines} protecting their \textbf{lands} and our shared \textbf{future}.
To avert catastrophe, we need to achieve zero global emissions, starting by halving them by 2030. \textbf{Governments} must align their targets with 1.5°C \textbf{limits}, especially as we approach COP26, where bold commitments are essential.
Financial \textbf{institutions} have a critical role : they must divest from fossil \textbf{fuels} without resorting to greenwashing, ensuring their actions truly \textbf{support} a sustainable \textbf{path}.
Fixing our broken food \textbf{system} is key, which \textbf{means} ending deforestation and promoting plant-based diets to reduce emissions and preserve \textbf{biodiversity}.
We also need to transform transport \textbf{systems} to cut pollution and build cleaner alternatives.
Protecting at least 30 % of \textbf{ecosystems} worldwide is vital for maintaining the \textbf{planet} 's health and \textbf{resilience}. \textbf{Supporting} Indigenous \textbf{rights} is non-negotiable, recognizing their \textbf{leadership} in \textbf{environmental} \textbf{stewardship}.
As we prepare for the \textbf{impacts} of \textbf{climate} change, we must do so justly, applying the polluter pays principle to hold those responsible accountable.
Solidarity is crucial, delivered through robust \textbf{climate} \textbf{finance} to \textbf{support} vulnerable \textbf{communities} globally.
We advocate for a just transition away from fossil \textbf{fuels}, with no new investments in this destructive industry.
Finally, we can leverage the COVID-19 recovery for a green \textbf{future}, \textbf{powered} by \textbf{people} coming together to \textbf{demand} and drive change.

% matched lemmas: biodiversity, climate, community, crisis, demand, ecosystem, environmental, finance, frontline, fuel, future, government, impact, institution, land, leadership, limit, mean, path, people, planet, power, resilience, resistance, right, solidarity, stand, stewardship, support, system
\end{textsample}
