\begin{textsample}{POS Dim 2 – persona\_gpt – Score 69.00 – t363\_gpt.txt}  \label{ex:f2_pos_002}
For weeks, the Indonesian \textbf{government} has repeated the same line about the devastating \textbf{floods} in Borneo : this is all because of heavy rainfall, an unavoidable natural disaster.
But when entire \textbf{communities} are submerged, \textbf{forests} are stripped bare, and rivers run black with mud and debris, it ’s clear that this is not just about rain.
This is about a broken \textbf{system} that has allowed \textbf{forests} to be destroyed in the name of \textbf{profit}, leaving \textbf{people} exposed and unprotected.
What is happening in Borneo is the direct result of years of deforestation driven by palm oil \textbf{plantations}, mining concessions, and the steady erosion of \textbf{environmental} \textbf{protections}.
When \textbf{forests} are cleared, the \textbf{land} loses its ability to absorb water.
Rain that once filtered slowly through dense \textbf{roots} and rich \textbf{soil} now rushes over hard, exposed \textbf{ground}, swelling rivers and triggering \textbf{floods} and landslides.
These are not “ natural ” disasters.
They are human-made.
Instead of confronting this \textbf{reality}, officials have tried to shift blame onto the \textbf{weather}.
But extreme rain alone does not explain why \textbf{floods} are getting worse, why they are hitting more \textbf{people}, more often, and with greater intensity.
The real story lies in satellite images showing shrinking \textbf{forest} cover, in the \textbf{expansion} of industrial \textbf{plantations} and mines, and in the \textbf{policies} that have opened the \textbf{door} to this \textbf{destruction}.
A key turning point was the Omnibus Law, which stripped away crucial \textbf{environmental} \textbf{safeguards}.
Among the \textbf{protections} it removed was the requirement to maintain at least 30 % \textbf{forest} cover in each watershed and island.
That threshold was not a \textbf{luxury} ; it was a basic line of \textbf{defense} against \textbf{floods}, erosion, and ecological collapse.
By eliminating it, the \textbf{government} has made it easier for \textbf{corporations} to clear \textbf{forests} and exploit \textbf{land} without regard for the consequences.
The Omnibus Law sends a clear message to companies : go ahead, expand.
Convert \textbf{forests} into \textbf{plantations}.
Carve up \textbf{land} for mines.
The law weakens oversight and \textbf{accountability}, while \textbf{communities} downstream are left to deal with the mud, the wrecked homes, the lost \textbf{livelihoods}.
It is a \textbf{policy} \textbf{choice} that prioritizes short-term corporate gain over long-term safety and planetary health.
As a Greenpeace campaigner, I have seen this \textbf{pattern} before.
In 2015, together with \textbf{allies} and \textbf{communities}, we took legal action to \textbf{challenge} destructive practices and weak enforcement.
That lawsuit win showed that \textbf{people} can \textbf{push} back and that the law can be used to defend \textbf{forests} and \textbf{human} \textbf{rights}.
It was a \textbf{moment} of hope, proof that organized \textbf{resistance} can \textbf{force} change even in the \textbf{face} of powerful \textbf{interests}.
But victories like that are not enough if new laws simply dismantle the \textbf{protections} we fought to secure.
The current \textbf{crisis} in Borneo is a warning of what happens when \textbf{environmental} \textbf{safeguards} are treated as obstacles instead of lifelines. \textbf{Forests} are not just trees to be cleared for \textbf{profit} ; they are living \textbf{systems} that regulate water, store carbon, shelter wildlife, and \textbf{support} \textbf{communities}.
Borneo is one of the most biodiverse places on Earth.
Its \textbf{forests} are home to countless species found nowhere else, and to Indigenous \textbf{peoples} whose \textbf{cultures} and \textbf{knowledge} are deeply intertwined with the \textbf{land}.
When these \textbf{forests} are destroyed, it is not only orangutans, hornbills, and rare plants that are at \textbf{risk}.
It is the entire web of \textbf{life}, including the \textbf{people} who depend on healthy \textbf{ecosystems} for clean water, food, and \textbf{protection} from disasters.
The \textbf{floods} are happening against the \textbf{backdrop} of a global \textbf{climate} \textbf{crisis} and the ongoing COVID-19 \textbf{pandemic}.
Both have exposed how fragile our \textbf{systems} are when we ignore \textbf{science} and put \textbf{profit} first.
The same model of extractive, fossil-fuelled growth that drives deforestation also drives \textbf{climate} \textbf{breakdown} and increases the \textbf{risk} of new diseases.
We cannot afford to treat these \textbf{crises} as separate.
They are \textbf{symptoms} of the same disregard for planetary \textbf{boundaries}.
Shifting away from this destructive \textbf{path} \textbf{means} rejecting the \textbf{narrative} that blames the sky while letting \textbf{corporations} off the hook.
It \textbf{means} \textbf{demanding} \textbf{policies} that keep \textbf{forests} \textbf{standing}, restore degraded \textbf{land}, and stop handing out concessions that sacrifice \textbf{communities} for export \textbf{commodities}.
It \textbf{means} embracing renewable energy and sustainable \textbf{livelihoods} instead of doubling down on \textbf{coal}, oil, and deforestation-based industries.
This is not just the responsibility of those living in Borneo.
It is a collective \textbf{struggle} that requires unity across regions and sectors : Indigenous \textbf{communities}, farmers, fishers, workers, urban residents, scientists, lawyers, and activists.
The 2015 lawsuit showed that when \textbf{people} come together, they can \textbf{challenge} entrenched \textbf{power}.
That same spirit of \textbf{solidarity} is needed now, on an even larger scale.
We must insist that the health of the \textbf{planet} is not negotiable. \textbf{Forest} cover requirements should be strengthened, not scrapped. \textbf{Environmental} \textbf{impact} \textbf{assessments} should be rigorous, not rubber stamps.
Laws must protect \textbf{people} and \textbf{nature}, not shield \textbf{corporations} from \textbf{accountability}.
Any recovery from the economic \textbf{impacts} of COVID-19 must be built around \textbf{resilience}, renewable energy, and \textbf{ecosystem} \textbf{protection}, not around the further \textbf{exploitation} of \textbf{land} and \textbf{forests}.
Borneo ’s \textbf{floods} are a stark \textbf{reminder} of the cost of \textbf{inaction} and denial.
Every hectare of \textbf{forest} cleared, every regulation weakened, every concession granted in a fragile watershed increases the \textbf{risk} of the next disaster.
The \textbf{choice} is between a \textbf{future} of recurring catastrophe and a \textbf{future} in which \textbf{forests}, rivers, and \textbf{communities} can thrive together.
The \textbf{government} can keep pointing to the clouds, but \textbf{people} on the \textbf{ground} know the truth.
The water that has swallowed homes and fields carries the evidence of deforestation and deregulation.
To honor those who are suffering now—and to prevent even greater \textbf{suffering} in the future—we must \textbf{stand} together to defend Borneo ’s \textbf{forests}, protect its \textbf{biodiversity}, and \textbf{push} for a rapid transition to renewable energy and truly sustainable development.
The \textbf{path} forward is clear : restore and protect the \textbf{forests}, strengthen \textbf{environmental} laws instead of tearing them down, and put the health of \textbf{people} and the \textbf{planet} at the \textbf{center} of every \textbf{decision}.
Only then will the rain once again be a blessing, not a threat.

% matched lemmas: accountability, ally, assessment, backdrop, biodiversity, boundary, breakdown, center, challenge, choice, climate, coal, commodity, community, corporation, crisis, culture, decision, defense, demand, destruction, door, ecosystem, environmental, expansion, exploitation, face, flood, force, forest, future, government, ground, human, impact, inaction, interest, knowledge, land, life, livelihood, luxury, mean, moment, narrative, nature, pandemic, path, pattern, people, planet, plantation, policy, power, profit, protection, push, reality, reminder, resilience, resistance, right, risk, root, safeguard, science, soil, solidarity, stand, struggle, suffering, support, symptom, system, weather
\end{textsample}
