\begin{textsample}{POS Dim 2 – persona\_grok – Score 28.00 – t476\_grok.txt}  \label{ex:f2_pos_032}
In the \textbf{heart} of Kampala, Uganda, Vanessa Nakate \textbf{stands} as a prominent \textbf{leader} in the Fridays for \textbf{Future} movement, drawing attention to the unequal toll of \textbf{climate} disasters on \textbf{women} across African \textbf{communities}.
These \textbf{crises} hit \textbf{women} hardest, amplifying their daily \textbf{struggles} in profound ways.
When \textbf{floods} ravage the \textbf{land}, they wipe out crops that families depend on, leaving \textbf{women} to shoulder the burden of starting food production anew.
This often \textbf{means} trekking long distances just to secure basic \textbf{survival} needs for their households. \textbf{Droughts} bring their own hardships, parching water sources and compelling \textbf{women} to haul heavy loads over vast stretches.
The physical \textbf{strain} is immense, frequently resulting in chronic back pain that lingers as a constant \textbf{reminder} of these \textbf{environmental} upheavals.
As primary caregivers for children, \textbf{women} confront the fallout of these disasters head-on : homelessness that uproots entire families, deep-seated trauma from \textbf{loss} and \textbf{displacement}, and heightened \textbf{vulnerabilities} to physical and sexual \textbf{violence} in unstable conditions.
The economic ripple effects are devastating too. \textbf{Losses} in subsistence farming \textbf{push} families into desperate measures, including \textbf{forcing} daughters into early marriages as a means of \textbf{survival}.
Pregnant \textbf{women} \textbf{face} even greater perils amid these \textbf{chaos}, with many enduring dangers that rob them of their \textbf{lives} or shatter their dreams for the \textbf{future}.
Yet, it 's \textbf{women} like these who are on the \textbf{frontlines} of \textbf{climate} action, and their efforts deserve our utmost \textbf{respect}.
By advocating against \textbf{climate} change, they give \textbf{voice} to millions whose stories must be heard and \textbf{acted} upon.

% matched lemmas: act, chaos, climate, community, crisis, displacement, drought, environmental, face, flood, force, frontline, future, heart, land, leader, life, loss, mean, push, reminder, respect, stand, strain, struggle, survival, violence, voice, vulnerability, woman
\end{textsample}
