\begin{textsample}{POS Dim 2 – persona\_gemini – Score 20.00 – t110\_gemini.txt}  \label{ex:f2_pos_047}
A recent media story highlighted an outdoor brand founder who pledged all of the company 's equity to combat the \textbf{climate} \textbf{crisis}, making Earth the only shareholder.
This is a call to choose action, hope, and \textbf{courage}.
It points toward a green and fair \textbf{future} built on \textbf{justice} and collaboration, where \textbf{people} and the \textbf{planet} are put before \textbf{profit}.
The \textbf{climate} and \textbf{biodiversity} \textbf{crises} are evident.
In response, there are growing global \textbf{challenges} to neo-liberal capitalism.
This is especially true among \textbf{youth}, who are linking the economic \textbf{system} to \textbf{inequality} and \textbf{environmental} \textbf{destruction}.
The \textbf{environmental} movement is now calling for a focus on addressing these \textbf{root} causes by uniting with other activists and movements.
Hopeful alternatives are being put forward.
These include debt cancellation for the Global South, the implementation of progressive taxes, and an end to fossil \textbf{fuel} subsidies.
There is also a \textbf{push} to shift our focus beyond GDP to instead prioritize social and \textbf{environmental} well-being.
Real changes are already happening in resilient \textbf{communities} that emphasize \textbf{cooperation}, indigenous \textbf{knowledge}, and sovereignty, as well as in the actions of purpose-driven companies.

% matched lemmas: biodiversity, challenge, climate, community, cooperation, courage, crisis, destruction, environmental, fuel, future, inequality, justice, knowledge, people, planet, profit, push, root, system, youth
\end{textsample}
