\begin{textsample}{POS Dim 2 – persona\_gemini – Score 22.00 – t611\_gemini.txt}  \label{ex:f2_pos_042}
In Brasília, Indigenous Peoples from across Brazil gather each year for the Free Land Camp.
It is a time to share \textbf{knowledge}, offer mutual \textbf{support}, and \textbf{demand} that the \textbf{government} protect their \textbf{rights}.
This year, the gathering is bittersweet.
The administration of President Bolsonaro has weakened \textbf{environmental} \textbf{tools} and has not protected Indigenous \textbf{communities} from the \textbf{violence}, threats, and \textbf{land} invasions carried out by industries.
Indigenous Peoples hold constitutional \textbf{rights} to their traditional \textbf{lands}, which they have long fought to protect.
In \textbf{solidarity}, global activists have demonstrated at Brazilian embassies with banners, music, and \textbf{speeches}.
They are urging \textbf{people} to \textbf{stand} with these \textbf{forest} \textbf{guardians} to save the Amazon.
Since 2012, deforestation has been on the rise.
An area equivalent to two soccer fields is now cleared every minute.
This \textbf{destruction} threatens \textbf{livelihoods} and worsens the \textbf{climate} \textbf{breakdown}, leading to events like hurricanes and heat waves.
Indigenous \textbf{lands} are the best-protected \textbf{forests}, yet the \textbf{government} is proposing to halt the \textbf{recognition} of these \textbf{territories}.
This move would open them up to mining, logging, and agriculture.
Join the movement to \textbf{support} them.

% matched lemmas: breakdown, climate, community, demand, destruction, environmental, forest, government, guardian, knowledge, land, livelihood, people, recognition, right, solidarity, speech, stand, support, territory, tool, violence
\end{textsample}
