\begin{textsample}{POS Dim 2 – persona\_grok – Score 26.00 – t219\_grok.txt}  \label{ex:f2_pos_036}
As we look back on 2021, it 's clear that despite the \textbf{challenges}, \textbf{people} \textbf{power} and determined advocacy have delivered some remarkable victories for our \textbf{planet}.
These 10 inspiring \textbf{environmental} wins remind us of what 's possible when \textbf{communities}, \textbf{governments}, and \textbf{courts} \textbf{stand} up to protect our shared \textbf{future}.
They \textbf{fuel} our hope and build momentum as we head into 2022, ready to \textbf{push} for even greater change.
In Gambia, a destructive fishmeal plant that threatened local fisheries and \textbf{ecosystems} was halted, \textbf{safeguarding} vital marine \textbf{resources} for coastal \textbf{communities}.
New Zealand rejected proposals for seabed mining, preserving fragile ocean floors from irreversible damage and setting a strong precedent against exploitative practices.
China made a significant pledge to stop building new \textbf{coal} projects overseas, marking a crucial step in curbing global fossil \textbf{fuel} \textbf{expansion} and \textbf{supporting} cleaner energy transitions worldwide.
In Russia, Norilsk Nickel \textbf{faced} a historic fine for a massive Arctic oil spill, holding a major polluter accountable and highlighting the need for stricter \textbf{environmental} \textbf{protections} in vulnerable regions.
Mexico banned genetically modified corn and committed to phasing out glyphosate, protecting \textbf{biodiversity}, traditional farming, and public health from harmful agricultural chemicals.
Shell withdrew from the Cambo oil field in the UK, abandoning plans for new North Sea drilling and signaling a shift away from risky fossil \textbf{fuel} investments.
A Dutch \textbf{court} ordered Shell to slash its emissions by 45 % by 2030, delivering a landmark ruling that \textbf{forces} corporate responsibility in the fight against \textbf{climate} change.
The Keystone XL pipeline was canceled, preventing further \textbf{expansion} of tar sands oil infrastructure and averting potential harm to Indigenous \textbf{lands} and water sources.
In Indonesia, a \textbf{court} ruling mandated action to tackle Jakarta 's severe air pollution, compelling authorities to address this public health \textbf{crisis} and improve urban air quality.
Finally, a French \textbf{court} found the state negligent on \textbf{climate} action, \textbf{pushing} for stronger \textbf{government} commitments to reduce emissions and meet international \textbf{climate} goals.
These achievements show that progress is happening—driven by \textbf{grassroots} movements, legal battles, and bold \textbf{decisions}.
Let 's carry this energy forward into 2022, united in our efforts to defend the environment and secure a sustainable \textbf{world} for all.

% matched lemmas: biodiversity, challenge, climate, coal, community, court, crisis, decision, ecosystem, environmental, expansion, face, force, fuel, future, government, grassroots, land, people, planet, power, protection, push, resource, safeguard, stand, support, world
\end{textsample}
