\begin{textsample}{POS Dim 2 – persona\_grok – Score 25.00 – t217\_grok.txt}  \label{ex:f2_pos_038}
In 2021, the \textbf{world} witnessed a barrage of extreme \textbf{weather} events that underscored the escalating \textbf{climate} \textbf{crisis}.
Record-breaking cold waves gripped Madrid and Texas, bringing unprecedented snowfall and freezing temperatures that disrupted daily \textbf{life} and infrastructure.
Cyclone Eloise tore through Mozambique and neighboring countries, leaving widespread devastation in its wake with heavy rains, strong winds, and \textbf{flooding} that displaced \textbf{communities} and destroyed homes.
Beijing \textbf{faced} one of its worst sandstorms in years, choking the city in dust and reducing visibility to dangerous levels.
Massive \textbf{floods} inundated parts of Australia and Europe, submerging towns, causing landslides, and leading to significant \textbf{loss} of \textbf{life} and property.
Wildfires raged across Turkey, Greece, and California, consuming vast areas of \textbf{forest} and \textbf{forcing} evacuations amid intense heat and \textbf{drought} conditions.
Flash \textbf{floods} struck various regions in Asia, sweeping away villages and infrastructure in sudden, violent surges of water.
Meanwhile, the Amazon continued to suffer from rampant deforestation, accelerating the \textbf{loss} of this vital rainforest \textbf{ecosystem}.
In Patagonia, fires burned through unique landscapes, threatening \textbf{biodiversity} and local \textbf{communities}.
These events aren't isolated ; \textbf{climate} change is intensifying them, making \textbf{storms} more powerful, \textbf{heatwaves} more frequent, and \textbf{weather} \textbf{patterns} more unpredictable.
I 've heard stories from \textbf{people} who dismissed \textbf{climate} warnings for years—brushing off reports of rising temperatures or melting ice caps as distant problems.
But when a cold wave shut down their city or a wildfire approached their doorstep, the \textbf{reality} hit hard, turning abstract concerns into personal \textbf{emergencies}.
It 's clear we can't ignore this any longer.
We must phase out fossil \textbf{fuels} and transition to renewable energy sources like solar and wind. \textbf{Governments} and companies need to be held accountable for their role in \textbf{fueling} this \textbf{emergency}, \textbf{pushing} for \textbf{policies} that prioritize the \textbf{planet} over \textbf{profits}.
Together, we can \textbf{demand} the changes needed to confront the \textbf{climate} \textbf{crisis} head-on.

% matched lemmas: biodiversity, climate, community, crisis, demand, drought, ecosystem, emergency, face, flood, force, forest, fuel, government, heatwave, life, loss, pattern, people, planet, policy, profit, push, reality, storm, weather, world
\end{textsample}
