\begin{textsample}{POS Dim 4 – human – Score 25.00 – t835\_human.txt}  \label{ex:f4_pos_017}
Sailing across the nutrient rich \textbf{waters} of the West African Atlantic Ocean these past two months, I have been lucky enough to see an incredible array of \textbf{wildlife}. \textbf{Whales}, dolphins and pelicans, I have met them all in this trip.
And I was just as thrilled to encounter smaller \textbf{animals} like flying \textbf{fish} and gannets, and to \textbf{witness} the magic of the seawater that lights up a brilliant blue at night as dinoflagellates – tiny plankton – emit light as the Greenpeace \textbf{ship} ploughs through the waves.
For me and the \textbf{crew} of the Esperanza it has been a great honour to be able to visit these amazing places.
It has been a welcome break after spending weeks on the \textbf{seas} chasing the numerous illegal \textbf{fishing} \textbf{vessels} that exploit these fertile \textbf{waters}.
These were experiences which gave me enormous hope.
While \textbf{witnessing} the ugliest sides of industrial \textbf{fishing}, and the devastation it leaves behind, I have also seen signs of hope.
The extraordinary \textbf{beauty} of nature here, and the lifestyle of respect for nature that still exists in some of these remote places, strengthens my commitment to help save these places, and strengthens my resolve that we can save them.
Act now to protect this unique \textbf{beauty}.
Sign our petition to demand an efficient and sustainable regional management of \textbf{fisheries} in West Africa.
Pavel Klinckhamers is an \textbf{Oceans} campaigner with Greenpeace Netherlands onboard the Esperanza ( Originally published by Greenpeace Africa on April 27, 2017 ) I am aboard the Greenpeace Esperanza, on a mission to investigate the poor regulations and overfishing of the \textbf{area} by industrial \textbf{fishing} \textbf{vessels}.
I have seen awful things.
But I have also been overwhelmed by the \textbf{beauty} of these \textbf{oceans}.
The current mission has brought us to the \textbf{region} for two and a half months, bringing us from the deep \textbf{waters} of the \textbf{islands} of Cabo Verde in the \textbf{north} \textbf{west}, to the desert of Mauritania, to the tropics of Guinea Bissau and Sierra Leone in the south.
And it has been amazing.
In the colourful coral \textbf{reefs} in the deep \textbf{waters} of Cabo Verde we saw quantities of moray eels, spiny lobsters, soldier \textbf{fish} and more.
Off the \textbf{coast} of Mauritania, the \textbf{whales} I had seen in a previous trip still swim here and the dolphins that love to play at the bow of the \textbf{ship} seem to have multiplied in number – we have seen \textbf{thousands} so far in this trip.
All of this \textbf{life} is \textbf{fed} by a process called upwelling, where the cool, nutrient-rich \textbf{waters} of the 4000 meter deep \textbf{ocean} are pumped up to the \textbf{surface}.
That is what makes West Africa ’s \textbf{oceans} so full of \textbf{life}.
We also saw the \textbf{beauty} of the land, especially around the remote \textbf{island} communities of the Bijagos archipelago in Guinea Bissau and the Turtle \textbf{islands} in Sierra Leone.
They are flanked by mangroves and pearly white \textbf{beaches} and are so remote that the people still live in symbiosis with nature.
They are also places where special \textbf{animals} like the small marine hippo and the manatee, also known as the ‘ \textbf{sea} cow ’, can still find a refuge.
The mangroves are dense forests that grow in salt \textbf{water} and, as major carbon sinks, are an important ally in our fight against climate change.
It is important that they are protected and flourish.
The white \textbf{beaches} in this \textbf{area} are not only postcard-idyllic, they are also the most important breeding grounds in all of Africa for the green \textbf{sea} \textbf{turtle}, an endangered \textbf{species}.
All this natural \textbf{beauty} \textbf{lives} alongside the colourful bustle of West African \textbf{life}, where the people dress in lively patterned clothes and \textbf{fish} in brightly decorated canoe-like \textbf{vessels} known as pirogues.
Towns and settlements here are alive with the sound of the fabulous local music and the laughs and smiles of local residents, in spite of the many adversities they face.

% matched lemmas: animal, area, beach, beauty, coast, crew, feed, fish, fishery, fishing, island, life, north, ocean, reef, region, sea, ship, species, surface, thousand, turtle, vessel, water, west, whale, wildlife, witness
\end{textsample}
