\begin{textsample}{NEG Dim 1 – human – Score 4.00 – t961\_human.txt}  \label{ex:f1_neg_007}
Most people have heard about the Amazon rainforest and how we desperately need to protect it.
But there ’s a lesser-known, massive forest to the north that ’s under serious threat right now.
The global Boreal Forest stretches across the northern hemisphere through North America, Russia, Japan and Scandinavia.
The Canadian part of this forest is under threat from a company you ’ve probably never heard of : Resolute Forest Products.
Resolute has been logging in Indigenous Peoples ’ territories without their consent, they ’ve needlessly destroyed critical habitat of the endangered woodland caribou, and they are suing Greenpeace staff to stop them from telling you about what the company is doing in the Boreal.
Resolute is not a household name, and they don't want to be.
But you can help change that.
If we can get 100,000 of us around the world to \#StandForForests and send a message to Resolute CEO Richard Garneau, we ’ll shine a massive spotlight that he can't shy away from.
The Boreal Forest doesn't get much press, even though it ’s the planet ’s largest ecosystem and largest living carbon absorber ( AKA air purifier ).
Resolute hopes that what happens in the Boreal, stays in the Boreal.
In 2013 even they sued Greenpeace and two campaigners for \$7,000,000 after we exposed their destructive practices.
They want us to go away.
Let Resolute CEO Richard Garneau know that the 100,000 of us are not going anywhere, we \#StandForForests.
Cristiana De Lia is a Forest Campaigner for Greenpeace Canada.

% matched lemmas: 
\end{textsample}
