\begin{textsample}{POS Dim 4 – persona\_grok – Score 20.00 – t313\_grok.txt}  \label{ex:f4_pos_032}
Deep in the remote Indian Ocean lies the Saya de Malha Bank, an underwater plateau as vast as Belgium.
This hidden gem is home to the world 's largest seagrass meadow, along with shallow corals and a thriving array of marine \textbf{life}.
Endangered \textbf{turtles} glide through its \textbf{waters}, while sperm \textbf{whales} and pygmy blue \textbf{whales} roam these \textbf{depths}.
Seagrass meadows like this one play a crucial role in capturing significant amounts of CO2, helping combat climate change.
They also act as vital nurseries for countless marine \textbf{species}, fostering biodiversity.
Yet, these essential \textbf{ecosystems} are in \textbf{decline} worldwide due to human \textbf{activity}.
The \textbf{threats} to Saya de Malha are stark.
Industrial \textbf{fishing} \textbf{operations}, including those by EU \textbf{vessels}, deploy purse seine \textbf{nets} and longlines in the \textbf{area}.
These \textbf{methods} have led to the overfishing of yellowfin tuna, pushing populations to unsustainable levels.
Worse still, they result in bycatch that harms \textbf{turtles}, \textbf{whales}, and \textbf{sharks}, endangering these \textbf{species} further.
To protect places like Saya de Malha, we need a strong Global Ocean Treaty.
This treaty would enable the creation of \textbf{sanctuaries} in international \textbf{waters}, \textbf{safeguarding} these vital \textbf{ecosystems} from exploitation.
Join us in this fight—sign the petition today to push for the \textbf{protections} our \textbf{oceans} desperately need.

% matched lemmas: activity, area, decline, depth, ecosystem, fishing, life, method, net, ocean, operation, protection, safeguard, sanctuary, shark, specie, species, threat, turtle, vessel, water, whale
\end{textsample}
