\begin{textsample}{POS Dim 4 – persona\_grok – Score 16.00 – t764\_grok.txt}  \label{ex:f4_pos_035}
I recently embarked on an unforgettable expedition to Antarctica aboard Greenpeace 's \textbf{ship}, the Arctic \textbf{Sunrise}.
The scenery was nothing short of stunning, with vast \textbf{penguin} colonies dotting pebble \textbf{beaches} and glittering \textbf{ice} floes stretching out across the horizon.
During my time there, I \textbf{witnessed} firsthand the profound impacts of climate change.
Events like the calving of the massive Larsen C iceberg highlighted the rapid changes, alongside widespread melting \textbf{ice} that poses serious \textbf{threats} to local \textbf{ecosystems} and \textbf{species}, such as the uniquely adapted moss that clings to \textbf{life} in this harsh environment.
Daily \textbf{life} on the \textbf{ship} was a mix of routine and unpredictability.
We spent time cleaning the \textbf{vessel}, attending meetings, and engaging in \textbf{activities} that were often dictated by the weather.
Seasickness was a common challenge amid the rough \textbf{conditions}.
Observing the \textbf{penguins} in their natural \textbf{habitat} was particularly moving.
They appeared strong and resilient, yet their fragility in the face of environmental pressures inspired a deep sense of urgency to protect them.
Greenpeace 's work during the expedition included conducting research with submersibles in the Weddell Sea, where we aimed to identify new \textbf{species}.
This research supports the push for an Antarctic Ocean \textbf{Sanctuary}, which would help \textbf{safeguard} the \textbf{region} 's \textbf{wildlife} from the \textbf{threats} posed by industrial krill \textbf{fishing}.
My journey to Antarctica started from Seoul and was arduous, but ultimately incredibly rewarding.

% matched lemmas: activity, beach, condition, ecosystem, fishing, habitat, ice, life, penguin, region, safeguard, sanctuary, ship, specie, sunrise, threat, vessel, wildlife, witness
\end{textsample}
