\begin{textsample}{POS Dim 4 – persona\_gemini – Score 14.00 – t764\_gemini.txt}  \label{ex:f4_pos_048}
My journey from Seoul to Antarctica was arduous, but it has been incredibly rewarding.
Onboard Greenpeace ’s Arctic \textbf{Sunrise}, I have \textbf{witnessed} stunning scenery, from \textbf{penguin} colonies gathered on pebble \textbf{beaches} to glittering \textbf{ice} floes.
Alongside this \textbf{beauty}, the impacts of climate change are visible.
We are seeing the consequences of melting \textbf{ice} and the calving of the Larsen C iceberg, which pose \textbf{threats} to \textbf{ecosystems} and \textbf{species} like the specially adapted moss found here.
The \textbf{penguins}, when seen in their natural \textbf{habitat}, appear strong, yet they are also fragile.
This inspires a powerful desire to protect them. \textbf{Life} on the \textbf{ship} has a daily rhythm of cleaning and meetings, and all of our \textbf{activities} are dependent on the weather.
We also have to contend with seasickness.
Our work here is vital.
Greenpeace is conducting research using submersibles in the Weddell Sea, with the goal of identifying new \textbf{species}.
This research supports the campaign for an Antarctic Ocean \textbf{Sanctuary}, which would \textbf{safeguard} the incredible \textbf{wildlife} here from the pressures of industrial krill \textbf{fishing}.

% matched lemmas: activity, beach, beauty, ecosystem, fishing, habitat, ice, life, penguin, safeguard, sanctuary, ship, specie, sunrise, threat, wildlife, witness
\end{textsample}
