\begin{textsample}{POS Dim 4 – persona\_gpt – Score 27.00 – t835\_gpt.txt}  \label{ex:f4_pos_028}
The bow of the Esperanza cuts through the deep-blue Atlantic off West Africa, and the first thing that hits you is how alive the \textbf{ocean} feels.
These are nutrient-rich \textbf{waters}, and it shows. \textbf{Whales} and dolphins \textbf{surface} around the \textbf{ship}, pelicans and gannets patrol the waves, and flying \textbf{fish} scatter from the hull like silver arrows.
At night, bioluminescent plankton shimmer in our wake, turning the \textbf{sea} into a trail of stars.
From the \textbf{deck}, this \textbf{beauty} can feel almost overwhelming.
It ’s a reminder of what ’s at \textbf{stake}.
Our journey here is not just to \textbf{witness} this richness, but to protect it.
We are chasing illegal \textbf{fishing} \textbf{vessels} and \textbf{documenting} the damage that overfishing is inflicting on these \textbf{waters} and on the communities that depend on them.
The contrast is stark : the \textbf{ocean} ’s abundance on one side, and the clear signs of its depletion on the other.
Below the \textbf{surface}, the diversity continues.
Coral \textbf{reefs} hide moray eels and lobsters among their crevices.
These \textbf{reefs} are part of a wider \textbf{web} of \textbf{life} \textbf{fed} by powerful upwellings that bring nutrients from the deep \textbf{ocean} to the \textbf{surface}.
These natural processes support entire \textbf{ecosystems}, from tiny plankton to large marine \textbf{mammals}.
Along the \textbf{coast}, mangroves line the \textbf{shore}.
Their tangled roots are not only nurseries for countless marine \textbf{species} but also important carbon sinks, quietly \textbf{storing} carbon and helping to buffer the climate crisis.
Nearby \textbf{beaches} play a different but equally crucial role : they are vital nesting grounds for endangered green \textbf{sea} \textbf{turtles}.
Watching these \textbf{animals} return to lay their eggs on the sand underscores how closely linked land and \textbf{sea} really are.
Out on remote \textbf{islands}, the surprises continue.
Marine hippos and manatees live in and around these coastal \textbf{waters}, sharing space with communities that have long lived in close symbiosis with nature.
Life here is vibrant and deeply connected to the \textbf{sea}.
Colorful attire brightens the shoreline, pirogues glide across the \textbf{water}, and music carries over the waves.
These scenes are not just picturesque ; they are living proof of cultures and \textbf{livelihoods} intertwined with healthy \textbf{oceans}.
Amid the grim reality of illegal \textbf{fishing} and the visible scars of overexploitation, it is this resilience and \textbf{beauty} that offer hope.
The \textbf{ocean} still has the capacity to recover if we give it the chance.
That is why calls for sustainable \textbf{fisheries} management are so urgent.
Protecting these \textbf{waters} means protecting \textbf{whales} and dolphins, \textbf{turtles} and \textbf{reefs}, mangroves and manatees—and the coastal communities whose futures are bound to the health of the \textbf{sea}.
You can help by adding your voice and signing the petition for sustainable \textbf{fisheries} management.
Each signature is a step toward giving these \textbf{waters}, and the people and \textbf{wildlife} who depend on them, a fighting chance.

% matched lemmas: animal, beach, beauty, coast, deck, document, ecosystem, feed, fish, fishery, fishing, island, life, livelihood, mammal, ocean, reef, sea, ship, shore, specie, stake, store, surface, turtle, vessel, water, web, whale, wildlife, witness
\end{textsample}
