\begin{textsample}{POS Dim 4 – persona\_gemini – Score 19.00 – t835\_gemini.txt}  \label{ex:f4_pos_042}
From the \textbf{deck} of the Greenpeace \textbf{ship} Esperanza, I ’ve been sailing through the nutrient-rich Atlantic \textbf{waters} of West Africa.
It is a place of incredible \textbf{life}.
We have encountered \textbf{whales} and dolphins, watched pelicans and gannets dive for food, and seen flying \textbf{fish} skim the waves.
At night, the \textbf{water} comes alive with the glow of bioluminescent plankton.
Our mission here is to chase illegal \textbf{fishing} \textbf{vessels}, and we have \textbf{witnessed} the devastation caused by overfishing.
Yet, amidst this, it is the \textbf{beauty} of nature that provides hope.
Below the \textbf{surface}, we have seen coral \textbf{reefs} that are home to moray eels and lobsters.
These \textbf{ecosystems} are \textbf{fed} by the natural upwelling of nutrients from the deep.
Onshore, the mangroves serve as vital carbon sinks, and the \textbf{beaches} are essential for endangered green \textbf{sea} \textbf{turtles} to lay their eggs.
On remote \textbf{islands}, we have found marine hippos and manatees.
We ’ve also met communities living in symbiosis with nature, their \textbf{lives} vibrant with colourful attire, pirogues, and music.
This \textbf{region} is a treasure.
To protect it, we must ensure its resources are managed correctly.
Please join us and sign the petition for sustainable \textbf{fisheries} management.

% matched lemmas: beach, beauty, deck, ecosystem, feed, fish, fishery, fishing, island, life, reef, region, sea, ship, surface, turtle, vessel, water, whale, witness
\end{textsample}
